---
title: "ggvis"
author: "Clément Viguier"
date: "17 juillet 2018"
output: html_document
---
## ggvis

```{r echo=F}
library(ggvis)
library(ggplot2)
library(tidyr)
```

This package is an extension of ggplot2 to enable faster design exploration for data visualisation.
 
For now it contains the custom geom_dash that allows to plot dashes instead of points.
Those can be rotated (aes_angle in radiant) or widden (aes_width) to encode additional information in comparison of geom_points.

It also allows distribution visualisation like geom_rug.

```{r echo=T}
iris %>% ggplot(aes(Species , Petal.Length)) +
  geom_dash(width = 0.8) +
  coord_fixed()
```


The geom_arc function allows rapic arc visualisation

```{r ech = T}

iris %>% ggplot(aes(Sepal.Length , Petal.Length, colour = Species)) +
  geom_arc(width = 0.8, aes(angle = Petal.Width ,radius = 0.1*Sepal.Width)) +
  coord_fixed()
```


Because these geoms do not use symbols, but explicit representation of geometric objects, they work better with fixed coordinates.
This can be ensured by addig  `+ coord_fixed()` to your ggplot call.

Further work is need to ensure all objects fit the frame of the plot that is currently computed from the x,y of the aesthetic.
